Linear regression for approximating real and synthetic data

### 2022-10-05 doc/paper/paper.tex

With the confidence that our methods work as expected on synthetic data, we turn our attention to the real elevation data.

>>>>

With the confidence that our methods work as expected on synthetic data, we turn our attention to the real elevation data. Here we find that all forms of regression struggle to model the data, which shows a limitation of linear regression. The data is simply to varied and noisy to be effectively modelled by a polynomial of low degree, and larger degrees are so computationally intensive to calculate that it is not possible to reach the degrees needed to approximate the terrain.
